---
title: "Coffee experiment anlysis"
output:
  github_document:
    toc: true
---

```{r}
library(tidyverse)
theme_set(theme_minimal())
```


## Assemble the design matrix

Load the fractional design...

```{r}
design <- read.csv('half_factorial_design_four.csv',stringsAsFactors = FALSE)
print(design)
```


...and the values of the factor levels

```{r}
levels <- read.csv('factor_levels.csv',stringsAsFactors = FALSE)
print(levels)
``` 


Reshape the design matrix so it is easier to join with the levels

```{r}
design_long <- pivot_longer(design,cols=c(
  'factor_1','factor_2','factor_3','factor_4'
), names_to="factor", values_to = "level")
head(design_long)
```


Join design with levels

```{r}
design_levels_long <- design_long %>% inner_join(levels, by = c("factor","level"))
head(design_levels_long)
```


Now reshape back to wide format

```{r}
design_levels <- pivot_wider(design_levels_long, id_cols='run', names_from = 'variable', values_from = 'value')
print(design_levels)
```

## Read in results data

```{r}
results <- read.csv('run_results.csv',stringsAsFactors = FALSE)
results_levels <- results %>% inner_join(design_levels, by= 'run')
str(results_levels)
```

### Quick look at the correlation between outcome variables

Plot our outcomes: acidity, bitterness, and overall enjoyment

```{r}
ggplot(results_levels,aes(acid,bitter,color=overall))+geom_point()+
  scale_color_gradient(high='red',low='blue')+
  xlim(c(0,10))+ylim(c(0,10))
```

Regress overall enjoyment on bitterness and acidity

```{r}
summary(lm(overall ~ acid * bitter, data=results_levels))
```

So, bitterness seems to contribute pretty much soley to my enjoyment of the coffee. 

Of course I was using the same blend of beans throughout (Holy Mountain from [Chromatic Coffee](https://www.chromaticcoffee.com/)).
Description of [Holy Mountain blend](https://www.chromaticcoffee.com/holy-mountain-blend/) from their site: 

> This year's Holy Mountain is resonant, and darkly bright, if you can somehow picture that. Imagine a heavy bodied, creamy and velvety shot of classic espresso with tropical fruit notes and a richly dark single origin cacao from Ecuador thats been roasted perfectly. It also makes a loud and dense cup of coffee. We're pretty focused on mouthfeel with this one so revel in its textural journey! A three bean blend with a PNG Kunjin base, a Honduras Parainema micro-lot bridge, and a robust and fruited Amazonian coffee our green buyer bought at auction where he got the #1, #2, #3, and #4 winners! Prepare for an awakening.


## Analysis of experimental results

### Acidity Main Effects

```{r}
acid_main_effects <- lm(acid ~ water_temp + grind_size + grams_coffee + steep_time, data=results_levels)
summary(acid_main_effects)
```

### Bitterness Main Effects

```{r}
bitter_main_effects <- lm(bitter ~ water_temp + grind_size + grams_coffee + steep_time, data=results_levels)
summary(bitter_main_effects)
```


### Overall main effects

```{r}
overall_main_effects <- lm(overall ~ water_temp + grind_size + grams_coffee + steep_time, data=results_levels)
summary(overall_main_effects)
```

### Subsequent models

Remove grind size variable and add two-way interaction terms


```{r}
overall_model2 <- lm(overall ~ water_temp*grams_coffee + water_temp*steep_time + steep_time*grams_coffee, data=results_levels)
summary(overall_model2)
```


Model above is saturated, remove interactions

```{r}
overall_model3 <- lm(overall ~ water_temp + grams_coffee + steep_time, data=results_levels)
summary(overall_model3)
```



## Initial conclusions

- Going through this experiment, I think I have learned what I want to achieve- a robust, bitter cup with lower acidity.
- More coffee beans in grams -> more bitterness, more acidity
- It looks like 200F water and shorter steep times may be better, but I think we need more data
- Looks like I will need to do this again to gather more data... not surprising